The Semantics and Implementation of \CEU: a Synchronous Reactive Language based on Esterel

### 2015-09-29 paper.tex
Revisao Terra

\begin{figure}[!htb]
 \centering
 \includegraphics[width=0.7\columnwidth]{terra}
\caption{Terra programming system basic elements.}
 \label{fig.terra}
\end{figure}

\CEU scripts in Terra cannot execute arbitrary \C code, instead, they rely on 
pre-built components that can be customized for different application domains.
%
Considering the domain of WSNs, Terra already provides components organized in 
four areas: radio communication, group management, data aggregation, and local 
operations (e.g., access to sensors and actuators).
%
When creating an instance of the \VM, the programmer can choose whether or not 
to include each component, setting different abstraction boundaries.
%
The generated \VM has to be preloaded into the embedded devices before they are 
physically distributed.

The communication between \CEU and the Terra components is mostly through 
events:
scripts make requests through \code{output} events and \code{await} answers 
through \code{input} events.
%
Terra also provides system calls for initialization and configuration of 
components.

@@

Considering the compilation process illustrated in Figure~\ref{fig.impl} for 
the \C backend, the main difference resides in the \emph{Code Generation}, 
which now outputs assembly instructions for the Terra \VM, instead of \C.

>>>>

\begin{figure}[!htb]
 \centering
 \includegraphics[width=0.5\columnwidth]{terra}
\caption{Terra programming system basic elements.}
 \label{fig.terra}
\end{figure}

\CEU scripts cannot execute arbitrary \C code, instead, they rely on pre-built 
components that can be customized for different application domains.
%
Considering the domain of WSNs, Terra already provides components organized in 
four areas: radio communication, group management, data aggregation, and local 
operations (e.g., access to sensors and actuators).
%
When creating an instance of the \VM, the programmer can choose whether or not 
to include each component, setting different abstraction boundaries for 
scripts.
%
The generated \VM has to be preloaded into the embedded devices before they are 
physically distributed.

The communication between scripts in \CEU and the components in the \VM is 
mostly through events:
scripts \code{emit} requests through \code{output} events and \code{await} 
answers through \code{input} events.
%
Terra also provides system calls for initialization and configuration of 
components.

@@

Considering the compilation process illustrated in Figure~\ref{fig.impl} for 
the \C backend, the main difference resides in the \emph{Code Generation} 
phase, which here outputs assembly instructions for the Terra \VM, instead of 
\C.
